{\includegraphics[width=3cm, height=2.5cm]{TechDoc/Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TechDoc/TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-04-28 TechDoc/TechDoc.tex
Update TechDoc.tex

\title{
{\includegraphics[width=3cm, height=2.5cm]{./Cran.jpg}}
\\
\includegraphics[width=7cm, height=1cm]{./TB.jpg}
\\
{Technical Documentation for TersectBrowser+}
}

\author{David Oluwasusi, Tanya Stead, Gregory Lupton, Gabrielle Baumberg \\ Supervised by: Dr. Tomasz Kurowski}

>>>>

\title{
{\includegraphics[width=3cm, height=2.5cm]{TechDoc/Cran.jpg}}
\\
\includegraphics[width=7cm, height=1cm]{TechDoc/TB.jpg}
\\
{Technical Documentation for TersectBrowser+}
}

\author{Extra author, David Oluwasusi, Tanya Stead, Gregory Lupton, Gabrielle Baumberg \\ Supervised by: Dr. Tomasz Kurowski}
